---
title: "Creating ZIP Code Choropleths with *choroplethrZip*"
author: "Ari Lamstein"
date: "April 16, 2015"
output: html_document
---

<!--
  %\VignetteEngine{knitr}
%\VignetteIndexEntry{a) US ZIP Choropleths}
-->

You can create a choropleth of US ZIP codes with the function `zip_choropleth`. Note that what is rendered are actually US Zip Code Tabulated Areas (ZCTAs) from the US Census Bureau, not US Postal Service ZIP codes. [This page](https://www.census.gov/geo/reference/zctas.html) from the Census Bureau explains the differences. See also `?zip.map` for more details.

Note that because of its size (~60MB) the `choroplethrZip` package is not hosted on CRAN. Rather, it is hosted on github [here](https://github.com/arilamstein/choroplethrZip). You can install the package by following the installation instructions on that page.

# Data Requirements

The data.frame that you provide to `zip_choropleth` must have one column named "region" and one column named "value". Your entries for "region" must **exactly** match how regions are named in the map which choroplethr uses.  These names are defined in the object `zip.regions` along with some useful metadata:

```{r, cache=TRUE}
library(choroplethrZip)

?zip.regions
data(zip.regions)
head(zip.regions)
```

In order to use choroplethr, you must use the naming convention in the "region" column of zip.regions. That is, you must use the string version of the ZIP code - i.e. you must include any leading zeroes. 

# Exploring Data

Like all choroplethr functions, `zip_choropleth` allows you to specify the scale with the `num_colors` parameter. What makes `zip_choropleth` unique is the number of zoom options. In addition to viewing all ZIPs in the country you can select ZIPs by State, County, Metropolitan Statistical Area (MSA) as well as manually specify a number of ZIPs.

### All ZCTAs in a State

Here is an example of viewing all ZCTAs in a State by using the `state_zoom` parameter:

```{r, cache=TRUE}
library(choroplethr)
library(choroplethrZip)

?df_pop_zip
data(df_pop_zip)

?zip_choropleth
zip_choropleth(df_pop_zip, 
               state_zoom="new york", 
               title="2012 New York State ZCTA Population Estimates",
               legend="Population")
```

### All ZCTAs in Selected Counties

Here is an example of using the `county_zoom` parameter to zoom in on the five Counties of New York City:

```{r, cache=TRUE}
# New York City is comprised of 5 counties: Bronx, Kings (Brooklyn), New York (Manhattan), 
# Queens, Richmond (Staten Island). Their numeric FIPS codes are:
nyc_fips = c(36005, 36047, 36061, 36081, 36085)
zip_choropleth(df_pop_zip,
               county_zoom=nyc_fips,
               title="2012 New York City ZCTA Population Estimates",
               legend="Population")
```

### Manually Selecting ZCTAs

Here is an example of using the `zip_zoom` parameter to manually select all ZCTAs in two neighborhoods in Manhattan:
```{r, cache=TRUE}
manhattan_les = c("10002", "10003", "10009")
manhattan_ues = c("10021", "10028", "10044", "10128")
zip_choropleth(df_pop_zip,
               zip_zoom=c(manhattan_les, manhattan_ues),
               title="2012 Lower and Upper East Side ZCTA Population Estimates",
               legend="Population")
```

### All ZCTAs in a Metropolitan Statistical Area (MSA)

Here is an example of using the `msa_zoom` parameter to zoom in on the entire New York Metropolitan Statistical Area (MSA):

```{r, cache=TRUE}
zip_choropleth(df_pop_zip,
               msa_zoom="New York-Newark-Jersey City, NY-NJ-PA",
               title="2012 NY-Newark-Jersey City MSA\nZCTA Population Estimates",
               legend="Population")
```

### All ZCTAs in the USA

Here is an example of viewing all ZCTAs in the country. While interesting to look at, this map has two problems: 1) it takes a few minutes to render and b) due to the large number (32,989) and irregular shape of ZCTAs, it can sometimes be hard to read. I have found that experimenting with the number of colors can be especially useful for this map.

```{r, cache=TRUE, warning=FALSE, echo=FALSE}
zip_choropleth(df_pop_zip,
               title="2012 ZCTA Population Estimates",
               num_colors=7,
               legend="Population")
```

# Advanced Options

Any customization outside the optional parameters presented above will require you to create a `ZipChoropleth` object.  choroplethr uses [R6](https://github.com/wch/R6) to take advantage of object-oriented programming.  Here is an example of using the `ggplot2_scale` on the base Choropleth object to customize the palette used.

```{r, cache=TRUE}
library(ggplot2)

choro = ZipChoropleth$new(df_pop_zip)
choro$title = "2012 ZCTA Population Estimates"
choro$ggplot_scale = scale_fill_brewer(name="Population", palette=2, drop=FALSE)
choro$set_zoom_zip(state_zoom="new york", county_zoom=NULL, msa_zoom=NULL, zip_zoom=NULL)
choro$render()
```
