<!--
  %\VignetteEngine{knitr}
%\VignetteIndexEntry{b) Choropleths of US Census ZCTA Data}
-->

# Mapping US Census ZCTA Data

You can make choropleths of selected demographic information from the US Census Bureau with the function `?zip_choropleth_acs`. It functions analogously to the other "_acs" functions in the main choroplethr package.  Please see the vignette "Mapping Census Data" on the [choroplethr CRAN page](http://cran.r-project.org/web/packages/choroplethr/index.html) for additional details.

Here are examples of looking at the median income of ZCTAs in New York State with the different zoom levels that `zip_choropleth_acs` supports:

## All ZCTAs in a State

```{r}
library(choroplethrZip)
# Median income of all ZCTAs in New York State
zip_choropleth_acs("B19301", state_zoom="new york")
```

## All ZCTAs in Selected Counties

```{r}
library(choroplethrZip)
# zoom in on all ZCTAs in the 5 counties (boroughs) of New York City
nyc_fips = c(36005, 36047, 36061, 36081, 36085)
zip_choropleth_acs("B19301", county_zoom=nyc_fips)
```

## Manually Selecting ZCTAs

```{r}
library(choroplethrZip)
# compare Manhattan's Lower East Side and Upper East Side
manhattan_les = c("10002", "10003", "10009")
manhattan_ues = c("10021", "10028", "10044", "10128")
zip_choropleth_acs("B19301", num_colors=1, zip_zoom=c(manhattan_les, manhattan_ues))
```

## All ZCTAs in the New York Metropolitan Statistical Area (MSA)

```{r}
library(choroplethrZip)
# show all ZCTAs in the New York Metropolitan Statistical Area (MSA)
zip_choropleth_acs("B19301", msa_zoom="New York-Newark-Jersey City, NY-NJ-PA")
```