---
title: "Zip Code Demographics with *choroplethrZip v1.3.0*"
author: "Ari Lamstein"
date: "April 28, 2015"
output: html_document
---

### Introduction

In a [previous](http://rpubs.com/arilamstein/zip-vignette-2) vignette I demonstrated how to use choroplethrZip to get and visualize data from the US Census Bureau. choroplethrZip version 1.3.0 introduces a data.frame `df_zip_demographics` which contains eight statistics from the 2013 5-year American Community Survey (ACS). Additionally, it introduces a function `?get_zip_demographics` which can get those same statistics from other ACS surveys.

As always, technically the regions are Zip Code Tabulated Areas (ZCTAS), not USPS ZIP Codes [(link)](https://www.census.gov/geo/reference/zctas.html).

### Data

Here are the statistics in `df_zip_demographics`:

```{r}
library(choroplethrZip)
data(df_zip_demographics)
?df_zip_demographics

colnames(df_zip_demographics)
```

### Visualization

Here is a program that visualizes the data for New York City as a choropleth map:

```{r, warning=FALSE}
# FIPS codes for the 5 counties (boroughs) of New York City
nyc_fips = c(36005, 36047, 36061, 36081, 36085)

# print a map for each column of the demographic data.frame
for (i in 2:ncol(df_zip_demographics))
{
  # set the data and title
  df_zip_demographics$value = df_zip_demographics[,i]
  title = paste0("2013 New York City ZCTA Demographics:\n",
                 colnames(df_zip_demographics[i]))
  
  # print the map
  choro = zip_choropleth(df_zip_demographics, title=title, county_zoom=nyc_fips)
  print(choro)
}
```
